---
title: "Shots"
author: 'Last update: 01.17.19'
output:
  html_document: default
  pdf_document: default
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(readxl)
library(DataComputing)
library(plotly)
library(knitr)
shots <- read_excel("rough.xlsx")
shots2 <- read_excel("rough2.xlsx")
shots$loc_f = factor(shots$loc,
                     levels=c('LL', 'LC', 'LR',
                              'ML', 'MC', 'MR',
                              'HL', 'HC', 'HR'))
shots$type_f = factor(shots$type, 
                      levels = c('ON', 'OFF',
                                 'B', 'G'))
shots$opp_f = factor(shots$opp,
                     levels = c('Colgate', 'Merrimack', 'Union', 
                                'Providence', 'Mercyhurst', 'Syracuse',
                                'RPI', 'RMU', 'Boston', 'Cornell', 
                                'Lindenwood'))
shots2$opp_f = factor(shots2$Opp,
                      levels = c('Colgate', 'Merrimack', 'Union', 
                                'Providence', 'Mercyhurst', 'Syracuse',
                                'RPI', 'RMU', 'Boston', 'Cornell',
                                'Lindenwood'))
shotcounts <-
  shots %>%
  group_by(game, 
           plr) %>%
  summarise(avg_count = n())

shottypecounts <-
  shots %>%
  group_by(game,
           plr,
           type_f) %>%
  summarise(avg_count = n())

onnetcounts <-
  shottypecounts[shottypecounts$type_f == 'ON', 1:4]

typeloc <-
  shots %>%
  group_by(type_f,
           loc_f) %>%
  summarise(avg_count = n())

typeplr <-
  shots %>%
  group_by(type_f,
           plr) %>%
  summarise(avg_count = n())

loc <-
  shots %>%
  group_by(loc_f) %>%
  summarise(avg_count = n())
  loc$total = sum(loc$avg_count)
  loc$prob = loc$avg_count/loc$total
  loc$perc = loc$prob*100

on <-
  typeloc[typeloc$type_f == "ON", 1:3]
  on$total = sum(on$avg_count)
  on$prob = on$avg_count/on$total
  on$perc = on$prob*100
  
off <-
  typeloc[typeloc$type_f == "OFF", 1:3]
  off$total = sum(off$avg_count)
  off$prob = off$avg_count/off$total
  off$perc = off$prob*100
  
blocked <-
  typeloc[typeloc$type_f == "B", 1:3]
  blocked$total = sum(blocked$avg_count)
  blocked$prob = blocked$avg_count/blocked$total
  blocked$perc = blocked$prob*100
  
goals <-
  typeloc[typeloc$type_f == "G", 1:3]
  goals$total = sum(goals$avg_count)
  goals$prob = goals$avg_count/goals$total
  goals$perc = goals$prob*100
  
goals$loc = factor(goals$loc_f,
                     levels=c('LL', 'LC', 'LR',
                              'ML', 'MC', 'MR',
                              'HL', 'HC', 'HR'))

strengthshots <-
  shots %>%
  group_by(type_f, strength) %>%
  summarise(avg_count = n())
```

#Number of Shot Attempts by Player
```{r, echo = FALSE, warning = FALSE, fig.width = 8, fig.height = 7}
ggplot(data = shots, 
       aes(x = reorder(plr,plr))) +
  ylab("Number of Shots") +
  xlab("Player") +
  geom_bar(stat = "count")
```

#Progression on Shots Attempted by Player
```{r, echo = FALSE, warning = FALSE, fig.width =8, fig.height = 7}
ggplot(data = shotcounts, 
       aes(x = game, 
           y = avg_count)) +
  ylab("Number of Shots") +
  xlab("Game Number") +
  geom_point() +
  facet_wrap(~plr, 
             ncol = 6) +
  stat_smooth(method = lm)
```

#Progression of Shots ON NET by Player and Game
```{r, echo = FALSE, warning = FALSE, fig.width = 8, fig.height = 7}
ggplot(data = onnetcounts,
       aes(x = game,
           y = avg_count)) +
  ylab('Number of Shots On Net') +
  xlab('Game Number') +
  geom_point() +
  facet_wrap(~plr, 
             ncol = 6) +
  stat_smooth(method = lm)
```

#FNS of Shots Attempted by Player
```{r, echo = FALSE, warning = FALSE, fig.width = 8, fig.height = 7}
fnsplr <-
  ggplot(data = shotcounts, 
       aes(y = avg_count, 
           x = reorder(plr, plr))) +
  ylab("Number of Shots") +
  xlab("Player") +
  geom_boxplot(aes(group = plr),
               fill = "lightblue", 
               alpha = 0.5)

fnsplr <- ggplotly(fnsplr)

fnsplr
```

#Number of Shot Attempts by Game
```{r, echo = FALSE, warning = FALSE, fig.width = 8, fig.height = 7}
ggplot(data = shots, 
       aes(x = game)) +
  ylab("Number of Shots") +
  xlab("Game Number") +
  geom_bar(stat = "count", colour = 'lightgray', alpha = 0.4) +
  geom_line(stat = 'count', color = 'red', size = 2)
```

# Number of Shot Attempts by Possession
```{r, echo = FALSE, warning = FALSE, fig.width = 8, fig.height = 7}
pos <- ggplot(data = shots2, aes(x = game)) +
  ylab("Number of Shot Attempts") +
  xlab("Game Number") +
  labs(colour = "Team") +
  geom_point(aes(y = attagainst)) +
  geom_line(aes(y = attagainst, color = "Opponent")) +
  geom_point(aes(y = attfor)) + 
  geom_line(aes(y = attfor, color = "Penn State"))

pos <- ggplotly(pos)

pos
```

# Number of Shot Attempts by Position and Game Result
```{r, echo = FALSE, warning = FALSE, fig.width = 8, fig.height = 7}
posres <- 
  ggplot(data = shots2, aes(x = game)) +
  ylab('Number of Shot Attempts') +
  xlab('Game Number') +
  geom_point(aes(y = attfor)) +
  geom_point(aes(y = attagainst)) +
  geom_line(aes(y = attfor), colour = 'blue') +
  geom_line(aes(y = attagainst), colour = 'red') +
  facet_wrap(~ result)

posres <- ggplotly(posres)

posres
```


#Shot Attempts by Player AND Location
```{r, fig.width = 8, fig.height = 7, echo = FALSE, warning = FALSE}
ggplot(data = shots, aes(x = type_f, fill = loc)) +
  ylab("Number of Shots") +
  xlab("Type of Shot") +
  geom_bar() +
  facet_wrap(~plr, ncol = 6)
```

#Frequency of Shot Type by Location
```{r, fig.width = 8, fig.height = 7, echo = FALSE, warning = FALSE}
ggplot(data = shots, 
       aes(x = type_f, 
           fill = type)) +
  ylab("Number of Shots") +
  xlab("Type of Shot") +
  geom_bar(stat = "count") +
  facet_wrap(~loc_f)
```

#Frequency of Shots by Location
##Overall
```{r, echo = FALSE, warning = FALSE, fig.width = 8, fig.height = 7}
all <- 
  ggplot(data = loc, aes(x = total, y = total, fill = prob,
                        text = paste('percent: ', perc, '%',
                                     '</br> total ', loc_f, ': ', avg_count))) +
  geom_bar(stat = 'identity', position = 'stack') +
  facet_wrap(~loc_f) +
  theme_void()

all <- ggplotly(all)

all
```

##Blocked
```{r, fig.width = 8, fig.height = 7, echo = FALSE, warning = FALSE}
b <- 
  ggplot(data = blocked, aes(x = type_f, y = total, fill = prob, 
                             text = paste("percent: ", perc, "%", "</br> total ", loc_f, ": ", avg_count))) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~loc_f) +
  theme_void()

b <- ggplotly(b)

b
```

##On net
```{r, fig.width = 8, fig.height = 7, echo = FALSE, warning = FALSE}
on <- 
  ggplot(data = on, aes(x = type_f, y = total, fill = prob,
                        text = paste('percent: ', perc, '%',
                                     '</br> total ', loc_f, ': ', avg_count))) +
  geom_bar(stat = 'identity', position = 'stack') +
  facet_wrap(~loc_f) +
  theme_void()

on <- ggplotly(on)

on
```

##Off net
```{r, fig.width = 8, fig.height = 7, echo = FALSE, warning = FALSE}
off <-
  ggplot(data = off, aes(x = type_f, y = total, fill = prob, 
                         text = paste("percent: ", perc, "%",
                                      "</br> total ", loc_f, ": ", avg_count))) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~loc_f) +
  theme_void()

off <- ggplotly(off)

off
```

##Goals
```{r, fig.width = 8, fig.height = 7, echo = FALSE, warning = FALSE}
g <-
  ggplot(data = goals, aes(x = type_f, y = total, fill = prob, 
                           text = paste("percent: ", perc, "%", "</br> total ", loc_f, ": ", avg_count))) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~loc) +
  theme_void()

g <- ggplotly(g)

g
```
